---
title: Carob report
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)

scrolltab <- function(data, caption, width="100%") {
  rownames(data) <- NULL
  kableExtra::kbl(data, caption=caption) |>
    kableExtra::kable_classic(full_width = F,  position = "right") |>
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))  |> 
    kableExtra::scroll_box(width=width, height="400px")
}

ktab <- function(data, caption) {
    kableExtra::kbl(data, caption=caption) |>
    kableExtra::kable_classic(full_width=FALSE) |> 
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
}

uri <- "doi:10.7910/DVN/RKUMXB"
group <- "fertilizer"

suri <- carobiner::simple_uri(uri)
huri <- carobiner:::http_address(uri)
http <- paste0('<a href="', huri, '">here</a>')
github <- paste0("https://github.com/reagro/carob/blob/master/scripts/", group, "/", suri, ".R")
script <- paste0('<a href="', github, '">R script</a>')

f <- paste0("data/clean/", group, "/", suri, ".csv")
if (!file.exists(f)) {
  knitr::knit_exit()
}
```

```{r setup2, include=FALSE}
d <- read.csv(f) 
m <- read.csv(gsub(".csv$", "_meta.csv", f))

treatments <- unique(d[ , grep("_fertilizer|lime|OM_applied", colnames(d))])
treatments <- treatments[order(treatments[,1], treatments[,2], treatments[,3]), ]
rownames(treatments) <- NULL

get_values <- function(x, label) {
  x <- unique(x)
  ifelse(length(x)==1, x, paste0(length(x), " ", label, "(", paste(sort(x), collapse=", "), ")"))
}

crop <- get_values(d$crop, "crops")
country <- get_values(d$country, "countries")

if (is.null(d$fertilizer_type) || all(is.na(d$fertilizer_type))) {
  ferts <- "unknown"
} else {
  uf <- strsplit(unique(d$fertilizer_type), "; ") |> unlist() |> unique()
  ferts <- paste0(sort(uf), collapse=", ")
}

locvars <- c("country", paste0("adm", 1:5), "location", "site", "longitude", "latitude")
i <- which(locvars %in% colnames(d))
locs <- unique(d[, locvars[i]])
if (all(c("longitude", "latitude") %in% colnames(locs))) {
  xy <- unique(locs[, c("longitude", "latitude")])
  xytxt <- paste0("for which we have ", nrow(xy), " unique mapped locations.")
  haveXY <- TRUE
} else {
  xytxt <- paste0("for which we have no coordinates.")
  xy <- cbind(0,0)[0,]
  haveXY <- FALSE
}
     
pub <- ifelse(is.na(m$publication), "", paste0('You can also consult the accompanying <a href="', carobiner:::http_address(carobiner::simple_uri(m$publication, reverse=FALSE)), '">paper</a>.'))
```


This report describes standardized data for "*`r m$title`*". These data were standardized on `r m$carob_date` by `r m$carob_contributor` with this `r script`. The original data are available `r http`. This is the full citation of the data set: 

`r m$data_citation`

`r pub`

The dataset has `r nrow(d)` records for `r crop` in `r country`. These are the first `r min(nrow(d), 25)` records: 

```{r tab1}
scrolltab(head(d, 25), "records")
```

</br>
The dataset has `r nrow(treatments)` fertilizer treatments: 

```{r tab2}
scrolltab(treatments, "treatments")
```

The fertilizer types used were: `r ferts`.

The observations are for `r nrow(locs)` locations, `r xytxt`

```{r map, include=haveXY}
locs <- locs[!is.na(locs$latitude), ]
if (nrow(locs) > 0) {
  suppressMessages(library(terra))
  crs <- terra::crs
  v <- terra::vect(locs, c("longitude", "latitude"), crs="+proj=longlat")
  terra::plet(v, cex=2, col="red")
}
```