---
title: Carob report
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)

scrolltab <- function(data, caption, width="100%") {
  rownames(data) <- NULL
  kableExtra::kbl(data, caption=caption) |>
    kableExtra::kable_classic(full_width = F,  position = "right") |>
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))  |> 
    kableExtra::scroll_box(width=width, height="400px")
}

ktab <- function(data, caption) {
    kableExtra::kbl(data, caption=caption) |>
    kableExtra::kable_classic(full_width=FALSE) |> 
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
}

group <- "crop_cuts"

f <- paste0("data/compiled/carob_", group, ".csv")
if (!file.exists(f)) {
  knitr::knit_exit()
}
```

```{r setup2, include=FALSE}
d <- data.table::fread(f) 

m <- data.table::fread(gsub(".csv$", "_metadata.csv", f))

get_values <- function(x, label) {
  x <- unique(x)
  ifelse(length(x)==1, x, paste0(length(x), " ", label, " (", paste(sort(x), collapse=", "), ")"))
}

crop <- get_values(d$crop, "crops")
country <- get_values(d$country, "countries")
nsources <- length(unique(d$dataset_id))


#locvars <- c("country", paste0("adm", 1:5), "location", "site", "longitude", "latitude")
#i <- which(locvars %in% colnames(d))
#locs <- unique(d[, locvars[i]])

locs <- d[, c("dataset_id", "longitude", "latitude")]
noxy <- is.na(locs$latitude) | is.na(locs$longitude)
xy <- na.omit(unique(locs)) #[, c("longitude", "latitude")])

if (nrow(xy) > 0) {
	xytxt <- paste0("for which we have ", nrow(xy), " unique mapped locations.")
	if (any(noxy)) {
		xytxt <- paste(xytxt, sum(noxy), "records do not have coordinates.")
	}	
	haveXY <- TRUE
	xy$dataset_id <- paste0("<a href='https://carob-data.org/reports/", group, "/", xy$dataset_id, ".html'>", xy$dataset_id, "</a>")
} else {
	xytxt <- paste0("for which we have no coordinates.")
	xy <- cbind(0,0)[0,]
	haveXY <- FALSE
}

if (grepl("trials", group)) {
	varieties <- unique(d[, c("variety", "variety_code")])
    vartxt <- paste(" These are trial data for", nrow(varieties), "varieties.") 
} else {
	vartxt <- ""
}
   
```

This report describes the the Carob "*`r group`*" group. 
</br>

This dataset combines `r nsources` standardized individual data [sources](https://carob-data.org/done.html). It has has `r nrow(d)` records and `r ncol(d)` variables for `r crop` in `r country`. `r vartxt`

</br>
These are the first `r min(nrow(d), 25)` records: 

```{r tab1}
scrolltab(head(d, 25), "records")
```


</br>
You can see the contributing datasets [here](https://carob-data.org/done.html) if you use the search term for `r paste0("[", group,"]")`.

</br>
We have `r nrow(locs)` observations, `r xytxt`
</br></br>


```{r map, include=haveXY}
if (nrow(xy) > 0) {
  suppressMessages(library(terra))
  crs <- terra::crs
  v <- terra::vect(xy, c("longitude", "latitude"), crs="+proj=longlat")
  terra::plet(v, cex=2, col="red")
}
```

</br>
The data are further summarized in the table below


```{r summary, fig.width=6}
d$longitude <- d$latitude <- d$dataset_id <- d$trial_id <- d$record_id <- NULL
dfs <- summarytools::dfSummary(
  d, varnumbers=FALSE, graph.magnif=0.75, 
  max.string.width=20, display.labels=FALSE, valid.col=FALSE)
summarytools::view(dfs, method = "render", 
              report.title="", max.tbl.height = Inf)
```

